Fixing Vulnerabilities Potentially Hinders Maintainability

### 2021-02-03 paper/emse20.tex
small fix

\textit{\textbf{RQ3: What is the impact of security changes versus regular 
changes on the maintainability of open-source software?}}
The impact of security and regular changes on software maintainability 
is presented in Figure~\ref{fig:secvsreg}. In this section, 
we present a comparison of security patches with 
two different baselines of regular changes: \emph{random-baseline},
a dataset of random regular changes;
and \emph{size-baseline}, a dataset of  
regular changes with the same size as security 
patches. Our hypothesis in this research question is
that \emph{Security patches hinder more maintainability and 
need more attention than regular changes on software maintainability}.

>>>>

\textit{\textbf{RQ3: What is the impact of security changes versus regular 
changes on the maintainability of open-source software?}}
The impact of security and regular changes on software maintainability 
is presented in Figure~\ref{fig:secvsreg}. In this section, 
we present a comparison of security patches with 
two different baselines of regular changes: \emph{random-baseline},
a dataset of random regular changes;
and \emph{size-baseline}, a dataset of  
regular changes with the same size as security 
patches. Our hypothesis in this research question is
that \emph{Security patches hinder more software maintainability and 
need more attention than regular changes}.
